\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\csharp}{C{\nolinebreak[4]\raisebox{.6ex}{\#}}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeEducationHeader}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
        \textit{\small#5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeAward}[2]{
  \vspace{-1pt}
    \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-20pt}
}

\newcommand{\resumeJobDesc}[1]{
  \item\small{{ #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Matthew Coming} 	& MatthewComing.com \\
  Dallas, Texas 					& MatthewComing@gmail.com\\
  							& +1 (979) 240-1776 \\
  
\end{tabular*}
\vspace{-10pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeader
      {Texas A\&M, College of Engineering}{College Station, Texas}
      {Bachelor of Science in Computer Science;  GPA: 3.7}{Aug 2017 -- Present}
      {Minor in CyberSecurity; Graduating May 2021}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
     \begin{itemize}[leftmargin=*]
             \item\textbf{Languages}: C++, \csharp, JavaScript, Java, Bash
                     \vspace{-7pt}
             \item\textbf{Software}: Docker, VMWare, VirtualBox, ffmpeg
                     \vspace{-7pt}
             \item\textbf{Collaboration}: Git, Jira, Confluence, Agile Software Development
                     \vspace{-7pt}
             \item\textbf{IDEs}: Vim, Visual Studio, XCode, Jupyter Notebook
                     \vspace{-7pt}
             \item\textbf{Operating Systems and Technologies}: Linux, Cloudfront, Elastic Beanstalk, S3, Route 53
     \end{itemize}

%-----------EXPERIENCE-----------------
\section{Employment History}
  \resumeSubHeadingListStart
    
    \resumeSubheading
    {L3Harris Technologies}{Mission Integration Division, Greenville, Texas}
    {Co--op Software Engineer [Active Secret Clearance]}{11 Months}
      
      \resumeItemListStart
        \resumeJobDesc{Member of a team responsible for maintaining, refactoring, developing, and documenting software for the internal research and development of intelligence and reconnaissance systems, namely mission management software.}
        \resumeItem{JavaScript and React}
          {Designed and wrote ReactJS UI components that communicated with a backend message bus through Google Protobuf messages.}
        \resumeItem{\csharp{ }and WinForms}
          {Designed and wrote application code to expand the capabilities of L3Harris ViewPoint.}
        \resumeItem{Security}
          {Used Fortify static code analysis to triage and fix security defects in a legacy code base.}
        \resumeItem{GIS}
          {Worked extensively with CesiumJS, an open source JavaScript library for creating 3D globes and maps, and ESRI ArcMap.}
      \resumeItemListEnd
      \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects and Interests}
\begin{itemize}[leftmargin=*]
                  \resumeItem{Real-time Computer Vision}{Using ffmpeg and OpenCV to find and dynamically crop faces from streamed video.}
                  \vspace{-5pt}
                  \resumeItem{OpenGL, ThreeJS}{Pursuing the creation of algorithmic art by creating interesting animation or photos based off of real world data inputs.}
                  \vspace{-5pt}
                  \resumeItem{AWS}{Experimenting with different Amazon Web Services for small projects. Hosting MatthewComing.com using S3, Cloudfront, and Route 53. Created a small Elastic Beanstalk hosted calculator using API Gateway and Lambda.}
                  \vspace{-5pt}
\end{itemize}

%-----------ORGANIZATIONS-----------------
\section{Organizations and Clubs}
\resumeSubHeadingListStart
        \resumeAward{TAMU AutoDrive Challenge Team - Member}{Spring 2021}
         \vspace{0pt}
        \resumeItemListStart
                \resumeJobDesc{Real-time HD Map Verification -- Using the Robot Operating System(ROS) and rqt, a C++ qt-based framework for GUI development, this team created a system that allows a user to verify the correctness of a high definition map during the maneuvering of a self-driving car. }
        \resumeItemListEnd
        \resumeAward{TAMU CyberSecurity Club - Member}{Fall 2018, Spring 2019}
        \resumeAward{TAMU BUILD - Student Supervisor}{Fall 2018, Spring 2019}
        \vspace{0pt} % IKD MAN i guess this has to be here
        \resumeItemListStart
                \resumeJobDesc{BUILD is a student run organization at Texas A\&M University that transforms shipping containers into medical clinics and classrooms that are sent all around the world. The role of a Student Supervisor is to guide the work and oversee the safety of the hundreds of volunteers each semester.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Honors and Certification}
  \resumeSubHeadingListStart
    \resumeAward{Texas A\&M University Dean's Honor Award}{Fall 2017 / Fall 2018 / Spring 2020}
    \resumeAward{Texas A\&M University Distinguished Student Award}{Spring 2018 / Spring 2019}
\resumeSubHeadingListEnd
%----------------------------------
\end{document}
