\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\csharp}{C{\nolinebreak[4]\raisebox{.6ex}{\#}}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeEducationHeader}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
        \textit{\small#5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeAward}[2]{
  \vspace{-1pt}
    \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-20pt}
}

\newcommand{\resumeJobDesc}[1]{
  \item\small{{ #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Matthew Coming} & MatthewComing.com \\
  Dallas, Texas & MatthewComing@gmail.com\\
  & +1 (979) 240-1776 \\
  
\end{tabular*}
\vspace{-10pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeader
      {Texas A\&M, College of Engineering}{College Station, Texas}
      {Bachelor of Science in Computer Science;  GPA: 3.7}{Aug 2017 -- Present}
      {Minor in CyberSecurity; expected graduation Spring 2021}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
     \begin{itemize}[leftmargin=*]
             \item\textbf{Languages}: C++, \csharp, JavaScript, Java, Bash
                     \vspace{-7pt}
             \item\textbf{Software}: Docker, VMWare, VirtualBox
                     \vspace{-7pt}
             \item\textbf{Collaboration}: Git, Jira, Confluence, Agile Software Development
                     \vspace{-7pt}
             \item\textbf{IDEs}: VIM, Visual Studio, Intellij IDEA, XCode, Jupyter notebook
                     \vspace{-7pt}
             \item\textbf{Operating Systems and Technologies}: Ubuntu, CentOS, RHEL, AWS
     \end{itemize}

%-----------EXPERIENCE-----------------
\section{Employment History}
  \resumeSubHeadingListStart
    
    \resumeSubheading
    {L3Harris Technologies}{Greenville, Texas}
    {Co--op Engineer}{June 2019 -- Jan 2020}
      
      \resumeItemListStart
        \resumeJobDesc{Member of a team responsible for maintaining, refactoring, developing, and documenting software for internal research and development of intelligence and reconnaissance systems.}
        \resumeItem{JavaScript and React}
          {Designed and wrote ReactJS UI components as well as translation layer gateways to a back-end message bus.}
        \resumeItem{\csharp{ }and WinForms}
          {Designed and wrote application code to expand the capabilities of L3Harris ViewPoint.}
        \resumeItem{Security}
          {Used static code analysis to triage and fix security defects in legacy code base.}
        \resumeItem{GIS}
          {Worked closely with CesiumJS, an open source JavaScript library for creating 3D globes and maps.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Hakota Design}{Dallas, Texas}
      {Mentoree}{May 2018 -- Aug 2018}

     \resumeItemListStart
        \resumeItem{RST, \LaTeX, Markdown}
          {Created professional business artifacts with Latex, software spec. sheets in markdown, and self-documentation for python with RST.}
        \resumeItem{Git}
          {Learned the Git-Flow work flow to build a portfolio on GitHub.}
        \resumeItem{Preciate Quality Assurance}
          {Tested and documented the Preciate app's android and SMS user experience.}
        \resumeItem{UML}
          {Created use-case and sequence diagrams using open-source PlantUML.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects and Interests}
\begin{itemize}[leftmargin=*]
                  \resumeItem{AWS}{Experimenting with different Amazon Web Services for small projects. Hosting matthewcoming.com using S3, Cloudfront, and Route 53. Created a small Elastic Beanstalk hosted calculator using API Gateway and Lambda.}
                  \vspace{-5pt}
                  \resumeItem{OpenGL}{Learning computer graphics by writing fragment and vertex shaders for game engine design.}
\end{itemize}

%-----------ORGANIZATIONS-----------------
\section{Organizations and Clubs}
\resumeSubHeadingListStart
        \resumeAward{TAMU CyberSecurity Club - Member}{Aug 2018 - May 2019}
        \resumeAward{TAMU BUILD - Student Supervisor}{Aug 2018 - May 2019}
        \vspace{3pt}
        \resumeItemListStart
                \resumeJobDesc{BUILD is a student run organization at Texas A\&M University that transforms shipping containers into medical clinics and classrooms that are sent all around the world. The role of a Student Supervisor is to guide the work and oversee the safety of the hundreds of volunteers each semester.}
        \resumeItemListEnd
\resumeSubHeadingListEnd
%\vspace{3pt}

%-----------AWARDS-----------------
\section{Honors and Certification}
  \resumeSubHeadingListStart
    \resumeAward{Texas A\&M University Dean's Honor Award}{Dec 2018, Dec 2017}
    \resumeAward{Texas A\&M University Distinguished Student Award}{May 2018}
    \resumeAward{Red Cross First Aid/CPR/AED Certification}{June 2017}
\resumeSubHeadingListEnd
\vspace{5pt}

%----------------------------------
\end{document}
